Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-09-23 referee.tex
Added a note about the Hartwig+15 paper.

>>>>

-From Tilmans paper, they find that Jcrit, which corresponds to the point where if a halo is exposed to a flux above that value then it provides conditions for supermassive star formation, is almost half as small as the jeans length approach to calculating Jcrit. They use the Wolcott-Green shielding factor that we use, but they use a different method for calculating the column density. Figure 5 shows the differences. But since they are finding that even more halos would be allowed to form star formation, then (if I'm getting this correctly), we would be underestimating the amount of potential star formation sites.
